---
title: "Checking Two sessions"
author: "Hao Lu"
date: "9/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

The peak PLV recorded at various locations (vertex, mastoid), calculated with Rdf_to_Figures jupyter notebook

## Goal

We want to check if the plv around 40-Hz which was shown in both sessions were similar, if so, we will be able to combine those two sessions in one analysis



```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
library(nlme)
library(emmeans)
```

```{r}

# load data
df = read.csv(file = 'L:/jupyter_projects/MultiChannelSSSR/Location_PLV_Both_Session.csv')
df
```


```{r}
# convert variables into factors

df$ID  %<>% as.factor()
df$ref %<>% as.factor()
df$freq  %<>% as.factor()
df$channel  %<>% as.factor()
df$Session  %<>% as.factor()
summary(df)
```

```{r}
df_l = df[df$freq==34.28,]
summary(df_l)
```

```{r}
options(contrasts = c("contr.sum", "contr.poly"))
```




```{r}
df_2 = df_l[(df_l$channel %in% c(37,47,64,65)),]
summary(df_2)
```
```{r}
m2.lme <- lme(PLV ~ Session*ref*channel,data = df_2, random = ~1|ID)
anova(m2.lme,type='marginal')
```

Results showed that there is no significant main effect of session nor significant interaction involving it